---
# This RMD ....
# Authors : Vijay Nagarajan NEI/NIH, Junseok Jang NEI/NIH
title: "`r title_extraction`" #Multi-Agent System Analysis Report"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: yes
    self_contained: false
    css: styles.css
---

```{r setup, include=FALSE}
options(knitr.duplicate.label = "allow")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.table.format = "html") # set to html table format
```

```{r packages, message=FALSE, warning=FALSE}
#Install and load required R packages. Install the packages if you do not already have them installed
library(rmarkdown)
library(openxlsx)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggh4x)
library(igraph)
library(dplyr)

#sessionInfo()
```

## 1. Integrated Analysis Results
This report summarizes the results of a multi-agent-AI-system (IAN) based analysis performed using the provided list of differentially expressed genes. Results after IAN integrated all the individual agents responses is provided below:

### 1.1. High-Level Summary
```{r high-level-summary}, results='asis', message=FALSE, warning=FALSE}
# Extract the High-Level Summary section content
high_level_summary <- stringr::str_extract(
  final_response,
  "(?s)(?<=High\\-Level Summary\\*\\*\\n\\n).*?(?=\\n\\n\\*\\*Step 7)"
)

# Check if the extraction was successful
if (is.na(high_level_summary)) {
  warning("Could not extract High-Level Summary content. Check the format of 'final_response' carefully.")
  high_level_summary <- "" # Assign an empty string to avoid further errors
}

cat(high_level_summary)
  
```

### 1.2. Affected Biological Processes
```{r affected-processes}, results='asis', message=FALSE, warning=FALSE}
affected_processes <- stringr::str_extract(
  final_response,
  "(?s)(?<=Integrate Agent Summaries, Pathways and other data\\*\\*\\n\\n).*?(?=\\n\\n\\*\\*Step 3|$)"
)

# Check if the extraction was successful
if (is.na(affected_processes)) {
  warning("Could not extract the section content. Check the format of 'final_response' carefully.")
  affected_processes <- ""  # Assign an empty string to avoid further errors
}

# Apply HTML formatting for font size and font family
#affected_processes <- paste0(
#  "<div style='font-size:16px; font-family: Arial, sans-serif;'>",
#  affected_processes,
#  "</div>"
#)

# Print the extracted section (for verification)
cat(affected_processes)
```

### 1.3. Potential Regulatory Networks
```{r regulatory_networks}, results='asis', message=FALSE, warning=FALSE}

# Extract the content from Step 4: Regulatory Network Analysis
regulatory_network_analysis <- stringr::str_extract(
  final_response,
  "(?s)(?<=Regulatory Network Analysis\\*\\*\\n\\n).*?(?=\\n\\n\\*\\*Step 5)"
)

# Check if the extraction was successful
if (is.na(regulatory_network_analysis)) {
  warning("Could not extract the Regulatory Network Analysis section. Check the format of 'final_response' carefully.")
  regulatory_network_analysis <- "" # Assign an empty string to avoid further errors
}

# Extract the "Potential Upstream Regulators" section
potential_upstream_regulators <- stringr::str_extract(
  final_response,
  "(?s)(?<=Potential Upstream Regulators:\\*\\*\\n\\n).*?(?=\\n\\n\\*\\*Similar Systems)"
)

# Check if the extraction was successful
if (is.na(potential_upstream_regulators)) {
  warning("Could not extract the Potential Upstream Regulators section. Check the format of 'final_response' carefully.")
  potential_upstream_regulators <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(regulatory_network_analysis)

# Print the extracted content (for verification)
cat(potential_upstream_regulators)

```

### 1.4. Potential Hub Genes
```{r hub_genes}, results='asis', message=FALSE, warning=FALSE}
# Extract the content of Step 5: Further Analysis
step5_content <- stringr::str_extract(
  final_response,
  "(?s)(?<=\\*\\*Step 5: Further Analysis\\*\\*\\n\\n).*?(?=\\n\\n\\*\\*Step 6: High-Level Summary\\*\\*)"
)

# Check if the extraction was successful
if (is.na(step5_content)) {
  warning("Could not extract the Step 5 Further Analysis section. Check the format of 'final_response' carefully.")
  step5_content <- "" # Assign an empty string to avoid further errors
}


# Split the step5_content string by newline
lines <- unlist(strsplit(step5_content, "\n"))

# Find the line that contains "**Hub Gene Identification:**"
hub_gene_index <- grep("\\*\\*Hub Gene Identification:\\*\\*", lines)

# Find the line that contains "**Novelty Exploration:**"
novelty_index <- grep("\\*\\*Novelty Exploration:\\*\\*", lines)

# Check if both markers were found
if (length(hub_gene_index) > 0 && length(novelty_index) > 0) {
  # Extract the lines between the Hub Gene Identification marker and the Novelty Exploration marker
  hub_gene_lines <- lines[(hub_gene_index[1] + 1):(novelty_index[1] - 1)]

  # Combine the extracted lines into a single string, preserving newlines
  hub_gene_text <- paste(hub_gene_lines, collapse = "\n")

  # Print the extracted text
  cat(hub_gene_text)
} else {
  # Handle the case where one or both markers were not found
  hub_gene_text <- ""
  if (length(hub_gene_index) == 0) {
    warning("Could not find the Hub Gene Identification section.")
  }
  if (length(novelty_index) == 0) {
    warning("Could not find the Novelty Exploration section.")
  }
}

```

### 1.5. Similar Systems
```{r similar_systems}, results='asis', message=FALSE, warning=FALSE}
# Find the indices of "Similar Systems:" and "Hub Gene Identification:"

# Find the line that contains "**Similar Systems:**"
similar_systems_index <- grep("\\*\\*Similar Systems:\\*\\*", lines)

# Find the line that contains "**Hub Gene Identification:**"
hub_gene_index <- grep("\\*\\*Hub Gene Identification:\\*\\*", lines)

# Check if both markers were found
if (length(similar_systems_index) > 0 && length(hub_gene_index) > 0) {
  # Extract the lines between the Similar Systems marker and the Hub Gene Identification marker
  similar_systems_lines <- lines[(similar_systems_index[1] + 1):(hub_gene_index[1] - 1)]

  # Combine the extracted lines into a single string, preserving newlines
  similar_systems_text <- paste(similar_systems_lines, collapse = "\n")

  # Print the extracted text
  cat(similar_systems_text)
} else {
  # Handle the case where one or both markers were not found
  similar_systems_text <- ""
  if (length(similar_systems_index) == 0) {
    warning("Could not find the Similar Systems section.")
  }
  if (length(hub_gene_index) == 0) {
    warning("Could not find the Hub Gene Identification section.")
  }
}
```

### 1.6. Novelty Exploration
```{r novelty, results='asis', message=FALSE, warning=FALSE}
# Find the line that contains "**Novelty Exploration:**"
novelty_index <- grep("\\*\\*Novelty Exploration:\\*\\*", lines)

# Check if the marker was found
if (length(novelty_index) > 0) {
  # Extract the lines from the Novelty Exploration marker to the end of the vector
  novelty_lines <- lines[(novelty_index[1] + 1):length(lines)]

  # Combine the extracted lines into a single string, preserving newlines
  novelty_text <- paste(novelty_lines, collapse = "\n")

  # Print the extracted text
  cat(novelty_text)
} else {
  # Handle the case where the marker was not found
  novelty_text <- ""
  warning("Could not find the Novelty Exploration section.")
}

```

### 1.7. Download Full Analysis Report

Download the Full Integrated IAN Analysis Report Here:

```{r final_response_file, results='asis', message=FALSE, warning=FALSE}
download_link <- paste0("<a href='final_response.txt'>Open full final_response.txt text in new tab</a>")
cat(download_link)
```

## 2. System Model
IAN takes the integrated full analysis report and the integrated system network data from each of the agents response and puts forward a system model, which includes the system overview, mechanistic model and an hypothesis.

### 2.1. System Model and Overview
The nodes in yellow are "Genes" found in our list of DEGs. The Nodes in blue are either "Term/Concept" nodes or "Genes" not in our list of DEGs (coming from ChEA instead).

```{r system_model, results='asis', message=FALSE, warning=FALSE}
system_model_network

# Extract the System Overview section content
system_overview <- stringr::str_extract(
  system_model_response,
  "(?s)(?<=\\*System Overview\\*\\n\\n).*?(?=\\n\\n\\*Potential Upstream)"
)

# Check if the extraction was successful
if (is.na(system_overview)) {
  warning("Could not extract the System Overview section. Check the format of 'system_overview' carefully.")
  system_overview <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(system_overview)
```

### 2.2. Mechanistic Model

```{r mechanistic_model, results='asis', message=FALSE, warning=FALSE}
# Extract the Mechanistic Model section content
mechanistic_model <- stringr::str_extract(
  system_model_response,
  "(?s)(?<=\\*Mechanistic Model\\*\\n\\n).*?(?=\\n\\n\\*System Model)"
)

# Check if the extraction was successful
if (is.na(mechanistic_model)) {
  warning("Could not extract the Mechanistic Model section. Check the format of 'final_response' carefully.")
  mechanistic_model <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(mechanistic_model)
```


### 2.3. Hypothesis

```{r hypothesis, results='asis', message=FALSE, warning=FALSE}
# Extract the Hypothesis section content
hypothesis <- stringr::str_extract(
  system_model_response,
  "(?s)(?<=\\*Hypothesis\\*\\n\\n).*?(?=$)"
)

# Check if the extraction was successful
if (is.na(hypothesis)) {
  warning("Could not extract the Hypothesis section. Check the format of 'final_response' carefully.")
  hypothesis <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(hypothesis)
```

### 2.4. Download System Model Report

Download the Full System Model Report Here:

```{r full_response_file, results='asis', message=FALSE, warning=FALSE}
download_link <- paste0("<a href='system_model.txt'>Open full system_model.txt text in new tab</a>")

cat(download_link)
```

## 3. KEGG Enrichment
IAN runs enrichment analysis, filters the significant terms, prepares metadata and generates the LLM based agent response, analyzing the data like a human expert.

### 3.1. Kegg Enrichment Results
KEGG pathway enrichment analysis results, filtered

```{r kegg_filtered}, message=FALSE, warning=FALSE}
# Load the final response from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"

kegg_filtered <- kegg_results
#kegg_filtered <- file.path(output_dir, "kegg_enrichment_filtered.txt")

# Read the data
#data <- read_tsv(kegg_filtered)
data <- kegg_filtered

# Sort data by pvalue
data <- data %>%
  arrange(pvalue)

# Calculate -log10(pvalue)
data <- data %>%
  mutate(neglog10p = -log10(pvalue))

paged_table(as.data.frame(data))
```

### 3.2. Kegg Enrichment Analysis Plot
KEGG pathway enrichment analysis results, filtered - plot

```{r kegg_filtered_plot, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
# Plot the data
# Keep only top 20 rows
data <- head(data, 20)

kegg_plot <- data %>%
  ggplot(aes(x = neglog10p, y = fct_reorder(Description, neglog10p))) +
  geom_col(fill = "peachpuff") +
  labs(
       x = "-log10(pvalue)",
       y = "Pathways",
       title = "Top Enriched KEGG Pathways"
       ) +
       theme_minimal()

print(kegg_plot) # Explicitly print the plot


# Save the plot to a file
plot_filename <- file.path(output_dir_path, "kegg_enrichment_plot.png")
ggsave(plot_filename, plot = kegg_plot, width = 8, height = 6, dpi = 300)

# Create the download link
download_link <- paste0("<a href='kegg_enrichment_plot.png' download>Download Plot as PNG</a>")

cat(download_link)

```

### 3.3. KEGG LLM Agent Response

```{r kegg_agent, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
# Load the agent responses from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#agent_response_file <- file.path(output_dir, "agent_responses.txt")

# Read the agent responses from the file, line by line
#agent_response_lines <- readLines(agent_response_file)

# Combine the lines into a single string
agent_response <- paste(agent_response_lines, collapse = "\n")

# Extract the Agent 2 summary section content
agent_2_summary <- stringr::str_extract(
  agent_response,
  "(?s)Agent 2:\\n\\*\\*1\\. Summary and Categorization:\\*\\*.*?\\n\\n(?=\\*\\*2\\. Known Roles and Upstream Regulators:)"
)
  
# Check if the extraction was successful
if (is.na(agent_2_summary)) {
  warning("Could not extract the Agent 2 summary section. Check the format of 'final_response' carefully.")
  agent_2_summary <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(agent_2_summary)

```

## 4. WikiPathway Enrichment
IAN runs enrichment analysis, filters the significant terms, prepares metadata and generates the LLM based agent response, analyzing the data like a human expert.

### 4.1. WikiPathway Enrichment Results
WikiPathway enrichment analysis results, filtered

```{r wp_filtered}, message=FALSE, warning=FALSE}
# Load the final response from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#wp_filtered <- file.path(output_dir, "wp_enrichment_filtered.txt")

# Read the data
#data <- read_tsv(wp_filtered)
data <- wp_results
  
# Sort data by pvalue
data <- data %>%
  arrange(pvalue)

# Calculate -log10(pvalue)
data <- data %>%
  mutate(neglog10p = -log10(pvalue))

paged_table(as.data.frame(data))
```

### 4.2. WikiPathway Enrichment Analysis Plot
WikiPathway enrichment analysis results, filtered - plot

```{r wp_filtered_plot}, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
# Plot the data
# Keep only top 20 rows
data <- head(data, 20)

wp_plot <- data %>%
  ggplot(aes(x = neglog10p, y = fct_reorder(Description, neglog10p))) +
  geom_col(fill = "mediumpurple3") +
  labs(
       x = "-log10(pvalue)",
       y = "Pathways",
       title = "Top Enriched WikiPathways"
       ) +
       theme_minimal()

print(wp_plot) # Explicitly print the plot

# Save the plot to a file
plot_filename <- file.path(output_dir_path, "wp_enrichment_plot.png")
ggsave(plot_filename, plot = wp_plot, width = 8, height = 6, dpi = 300)

# Create the download link
download_link <- paste0("<a href='wp_enrichment_plot.png' download>Download Plot as PNG</a>")

cat(download_link)

```

### 4.3. WikiPathway LLM Agent Response

```{r wp_agent, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
# Load the agent responses from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#agent_response_file <- file.path(output_dir, "agent_responses.txt")

# Read the agent responses from the file, line by line
#agent_response_lines <- readLines(agent_response_file)

# Combine the lines into a single string
agent_response <- paste(agent_response_lines, collapse = "\n")

# Extract the Agent 2 summary section content
agent_1_summary <- stringr::str_extract(
  agent_response,
  "(?s)Agent 1:\\n\\*\\*1\\. Summary and Categorization:\\*\\*.*?\\n\\n(?=\\*\\*2\\. Known Roles and Upstream Regulators:)"
)

# Check if the extraction was successful
if (is.na(agent_1_summary)) {
  warning("Could not extract the Agent 2 summary section. Check the format of 'final_response' carefully.")
  agent_1_summary <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(agent_1_summary)

```

## 5. Reactome Enrichment

### 5.1. Reactome Pathways Enrichment Results
Reactome Pathways enrichment analysis results, filtered

```{r reactome_filtered}, message=FALSE, warning=FALSE}
# Load the final response from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#reactome_filtered <- file.path(output_dir, "reactome_enrichment_filtered.txt")

# Read the data
#data <- read_tsv(reactome_filtered)
data <- reactome_results

# Sort data by pvalue
data <- data %>%
  arrange(pvalue)

# Calculate -log10(pvalue)
data <- data %>%
  mutate(neglog10p = -log10(pvalue))

paged_table(as.data.frame(data))
```

### 5.2. Reactome Pathways Enrichment Analysis Plot
Reactome Pathways enrichment analysis results, filtered - plot

```{r reactome_filtered_plot}, message=FALSE, warning=FALSE}
# Plot the data

# Keep only top 10 rows
data <- head(data, 20)

# Define the maximum length for pathway names
max_length <- 75  # Adjust this value as needed

# Truncate the 'Description' column, adding "..." if truncated
data <- data %>%
  mutate(Description = ifelse(str_length(Description) > max_length,
                              paste0(str_sub(Description, 1, max_length), "..."),
                              Description))

data %>%
  ggplot(aes(x = neglog10p, y = fct_reorder(Description, neglog10p))) +
  geom_col(fill = "thistle") +
  labs(
       x = "-log10(pvalue)",
       y = "Pathways",
       title = "Top Enriched Reactome Pathways"
       ) +
       theme_minimal()

```

### 5.3. Reactome Pathways LLM Agent Response

```{r reactome_agent, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
# Load the agent responses from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#agent_response_file <- file.path(output_dir, "agent_responses.txt")

# Read the agent responses from the file, line by line
#agent_response_lines <- readLines(agent_response_file)

# Combine the lines into a single string
agent_response <- paste(agent_response_lines, collapse = "\n")

# Extract the Agent 3 summary section content
agent_3_summary <- stringr::str_extract(
  agent_response,
  "(?s)Agent 3:\\n\\*\\*1\\. Summary and Categorization:\\*\\*.*?\\n\\n(?=\\*\\*2\\. Known Roles and Upstream Regulators:)"
)

# Check if the extraction was successful
if (is.na(agent_3_summary)) {
  warning("Could not extract the Agent 2 summary section. Check the format of 'final_response' carefully.")
  agent_3_summary <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(agent_3_summary)

```

## 6. Gene Ontology Enrichment

### 6.1. Gene Ontology Enrichment Results

Gene Ontology enrichment analysis results, filtered

```{r go_filtered}, message=FALSE, warning=FALSE}
# Load the final response from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#go_filtered <- file.path(output_dir, "go_enrichment_filtered.txt")

# Read the data
#data <- read_tsv(go_filtered)
data <- go_results

# Sort data by pvalue
data <- data %>%
  arrange(pvalue)

# Calculate -log10(pvalue)
data <- data %>%
  mutate(neglog10p = -log10(pvalue))

paged_table(as.data.frame(data))
```

### 6.2. Gene Ontology Enrichment Analysis Plot
Gene Ontology enrichment analysis results, filtered - plot  - Top 20 Terms

```{r go_filtered_plot}, message=FALSE, warning=FALSE}
# Plot the data
# Keep only top 10 rows
data <- head(data, 20)

# Plot the data
plot <- data %>%
  ggplot(aes(x = neglog10p, y = fct_reorder(Description, neglog10p))) +
  geom_col(fill = "palegreen4") +
  labs(
       x = "-log10(pvalue)",
       y = "GO Terms",
       title = "Top Enriched GO Terms"
       ) +
       theme_minimal()+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 60), 
                   guide = "axis_nested", 
                   expand = expansion(mult = c(0.01, 0.01))) +
  theme(axis.text.y = element_text(lineheight = 0.8))
print(plot)

```

### 6.3. GO LLM Agent Response

```{r go_agent, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
# Load the agent responses from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#agent_response_file <- file.path(output_dir, "agent_responses.txt")

# Read the agent responses from the file, line by line
#agent_response_lines <- readLines(agent_response_file)

# Combine the lines into a single string
agent_response <- paste(agent_response_lines, collapse = "\n")

# Extract the Agent 5 summary section content
agent_5_summary <- stringr::str_extract(
  agent_response,
  "(?s)Agent 5:\\n\\*\\*1\\. Summary and Categorization:\\*\\*.*?\\n\\n(?=\\*\\*2\\. Known Roles and Upstream Regulators:)"
)

# Check if the extraction was successful
if (is.na(agent_5_summary)) {
  warning("Could not extract the Agent 2 summary section. Check the format of 'final_response' carefully.")
  agent_5_summary <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(agent_5_summary)

```

## 7. Transcription Factor Enrichment

### 7.1. Transcription Factor (ChEA) enrichment results
Transcription Factor (ChEA) enrichment analysis results, filtered

```{r chea_filtered}, message=FALSE, warning=FALSE}
# Load the final response from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#chea_filtered <- file.path(output_dir, "chea_enrichment_filtered.txt")

# Read the data
#data <- read_tsv(chea_filtered)
data <- chea_results

# Sort data by pvalue
data <- data %>%
  arrange(P.value)

# Calculate -log10(pvalue)
data <- data %>%
  mutate(neglog10p = -log10(P.value))

paged_table(as.data.frame(data))
```

### 7.2. Transcription Factor (ChEA) Enrichment Analysis Plot
Transcription Factor (ChEA) enrichment analysis results, filtered - plot

```{r chea_filtered_plot}, message=FALSE, warning=FALSE}
# Plot the data
# Keep only top 10 rows
data <- head(data, 20)

# Plot the data
plot <- data %>%
  ggplot(aes(x = neglog10p, y = fct_reorder(Term, neglog10p))) +
  geom_col(fill = "deepskyblue") +
  labs(
       x = "-log10(pvalue)",
       y = "Tanscription Factors",
       title = "Top Enriched Transcription Factors (ChEA)"
       ) +
       theme_minimal()+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 60), 
                   guide = "axis_nested", 
                   expand = expansion(mult = c(0.01, 0.01))) +
  theme(axis.text.y = element_text(lineheight = 0.8))
print(plot)

```

### 7.3. ChEA LLM Agent Response

```{r chea_agent, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
# Load the agent responses from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#agent_response_file <- file.path(output_dir, "agent_responses.txt")

# Read the agent responses from the file, line by line
#agent_response_lines <- readLines(agent_response_file)

# Combine the lines into a single string
agent_response <- paste(agent_response_lines, collapse = "\n")

# Extract the Agent 4 summary and regulatory network analysis section content
agent_4_summary <- stringr::str_extract(
  agent_response,
  "(?s)Agent 4:\\n\\*\\*1\\. Summary of Enriched Transcription Factors:\\*\\*.*?\\n\\n\\*\\*2\\. Regulatory Network Analysis:\\*\\*.*?\\n\\n(?=\\*\\*3\\. Novel Interactions:)"
)

# Check if the extraction was successful
if (is.na(agent_4_summary)) {
  warning("Could not extract the Agent 2 summary section. Check the format of 'final_response' carefully.")
  agent_4_summary <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(agent_4_summary)

```

## 8. Protein-Protein Interaction

```{r string_filtered}, message=FALSE, warning=FALSE}
# Load the final response from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#string_filtered <- file.path(output_dir, "string_interactions_filtered.txt")

# Read the data
#data <- read_tsv(string_filtered)
data <- string_results$interactions

# Sort data by pvalue
data <- data %>%
  arrange(desc(combined_score))

# Calculate -log10(pvalue)
#data <- data %>%
#  mutate(neglog10p = -log10(P.value))

# paged_table(as.data.frame(data))
```

### 8.1. Protein-Protein Interaction Network Analysis
The genes with high interactions scores are scored for network properties and a combined score is calculated to identify important genes. Top 10 genes are shown below.

```{r string_filtered_analysis}, message=FALSE, warning=FALSE}
library(igraph)
# Create graph object
graph <- graph_from_data_frame(data[, 1:2], directed = FALSE)

#Remove duplicate edges
graph <- igraph::simplify(graph, remove.multiple = TRUE, remove.loops = TRUE)

# Calculate network properties
degree <- degree(graph)
betweenness <- betweenness(graph)
closeness <- closeness(graph)
eigenvector_centrality <- eigen_centrality(graph)$vector

# Create a dataframe for network properties
node_properties <- data.frame(
  node = names(degree),
  degree = degree,
  betweenness = betweenness,
  closeness = closeness,
  eigenvector_centrality = eigenvector_centrality
)

# Add scaled properties
node_properties <- node_properties %>%
  mutate(degree_scaled = scale(degree),
         betweenness_scaled = scale(betweenness),
         closeness_scaled = scale(closeness),
         eigenvector_scaled = scale(eigenvector_centrality)
         )

# Calculate a combined property based on the scaled measures
scaled_cols <- grep("_scaled$", names(node_properties), value = TRUE)

node_properties <- node_properties %>% 
  mutate(combined_score_prop = rowMeans(node_properties[, scaled_cols], na.rm = TRUE))

# Sort genes by the combined score
important_genes <- node_properties %>% 
  arrange(desc(combined_score_prop))

# Reorder columns and move combined_score_prop to the second position
important_genes <- important_genes %>%
  dplyr::select(node, combined_score_prop, everything())

rownames(important_genes) <- NULL

# Display the important genes using paged_table with no row names
cat("## Important Genes based on Network Properties\n")
paged_table(head(important_genes, 10))

```

### 8.2. Protein-Protein Interaction Network Analysis Plot
Protein-Protein Interaction Network Analysis (STRING) results plot, filtered

```{r string_filtered_analysis_plot}, message=FALSE, warning=FALSE}

# Plot the combined score
plot <- head(important_genes, 20) %>%
  ggplot(aes(x = fct_reorder(node, combined_score_prop), y = combined_score_prop)) +
  geom_col(fill = "coral1") +
  labs(
    x = "Node",
    y = "Combined Score Property",
    title = "Combined Score Property for Top 20 Nodes"
  ) +
  coord_flip() + # Flip coordinates to have horizontal bars
  theme_minimal()
print(plot)

```

### 8.3. STRING LLM Agent Response

```{r string_agent, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
# Load the agent responses from the file
#output_dir <- "enrichment_results"
#output_dir <- "IAN_results"
#agent_response_file <- file.path(output_dir, "agent_responses.txt")

# Read the agent responses from the file, line by line
#agent_response_lines <- readLines(agent_response_file)

# Combine the lines into a single string
agent_response <- paste(agent_response_lines, collapse = "\n")

# Extract the Agent 6 summary and key interactions section content
agent_6_summary <- stringr::str_extract(
  agent_response,
  "(?s)Agent 6:\\n\\*\\*1\\. Summary of Interactions:\\*\\*.*?\\n\\n\\*\\*2\\. Key Interactions and Network Topology:\\*\\*.*?\\n\\n(?=\\*\\*3\\. Functional Implications and Upstream Regulators:)"
)

# Check if the extraction was successful
if (is.na(agent_6_summary)) {
  warning("Could not extract the Agent 2 summary section. Check the format of 'final_response' carefully.")
  agent_6_summary <- "" # Assign an empty string to avoid further errors
}

# Print the extracted content (for verification)
cat(agent_6_summary)

# Extract the ENTIRE Agent 6 section (all content) first
agent_6_all <- stringr::str_extract(
  agent_response,
  "(?s)Agent 6:.*" #Match everything after agent 6 until the end
)


# Check if the extraction of the entire Agent 6 section was successful
if (is.na(agent_6_all)) {
  warning("Could not extract the entire Agent 6 section. Check the format of 'agent_responses.txt' carefully.")
  agent_6_all <- "" # Assign an empty string to avoid further errors
}

# Now, extract the cross-analysis section from WITHIN the Agent 6 content
if (agent_6_all != "") { # Only try to extract the cross-analysis if we have Agent 6 content

  agent_6_cross_analysis <- stringr::str_extract(
    agent_6_all,
    "(?s)\\*\\*4\\. Cross-Analysis:\\*\\*.*?\\n\\n(?=\\*\\*5\\. Hypothesis Generation:|$)"
  )

  # Check if the extraction of the cross-analysis section was successful
  if (is.na(agent_6_cross_analysis)) {
    warning("Could not extract the Agent 6 cross-analysis section. Check the format of 'agent_responses.txt' carefully.")
    agent_6_cross_analysis <- "" # Assign an empty string to avoid further errors
  }

  # Print the extracted cross-analysis content (for verification)
  cat(agent_6_cross_analysis)

} else {
  warning("Skipping cross-analysis extraction because the entire Agent 6 section could not be extracted.")
  agent_6_cross_analysis <- ""
}

```


## 9. Full Integrated Network
The system representation from each of the 6 agents enrichment analysis responses are integrated to build the below network. This is the network that was used for deciphering the system model.

The nodes in blue are "Genes" found in our list of DEGs. The Nodes in yellow are either "Term/Concept" nodes or "Genes" not in our list of DEGs (coming from ChEA instead).

```{r integrated_network, results='asis', fig.width=8, fig.height=6, message=FALSE, warning=FALSE}

  full_integrated_network

```


## 10. Download
Here is the list of all original results, along with filtered results, computed results, integrated results and LLM responses:

```{r download_all}, results='asis', message=FALSE, warning=FALSE}

download_link_model <- paste0("<a href='system_model.txt'>Click to open system_model.txt in new tab</a>")
download_link_final <- paste0("<a href='final_response.txt'>Click to open final_response.txt in new tab</a>")
download_link_agents <- paste0("<a href='agent_responses.txt'>Click to open agent_responses.txt in new tab</a>")
download_link_kegg_original <- paste0("<a href='kegg_enrichment_original.txt'>Click to open kegg_enrichment_original.txt in new tab</a>")
download_link_kegg_filtered <- paste0("<a href='kegg_enrichment_filtered.txt'>Click to open kegg_enrichment_filtered.txt in new tab</a>")
download_link_wp_original <- paste0("<a href='wp_enrichment_original.txt'>Click to open wp_enrichment_original.txt in new tab</a>")
download_link_wp_filtered <- paste0("<a href='wp_enrichment_filtered.txt'>Click to open wp_enrichment_filtered.txt in new tab</a>")
download_link_reactome_original <- paste0("<a href='reactome_enrichment_original.txt'>Click to open reactome_enrichment_original.txt in new tab</a>")
download_link_reactome_filtered <- paste0("<a href='reactome_enrichment_filtered.txt'>Click to open reactome_enrichment_filtered.txt in new tab</a>")
download_link_chea_original <- paste0("<a href='chea_enrichment_original.txt'>Click to open chea_enrichment_original.txt in new tab</a>")
download_link_chea_filtered <- paste0("<a href='chea_enrichment_filtered.txt'>Click to open chea_enrichment_filtered.txt in new tab</a>")
download_link_string_original <- paste0("<a href='string_interactions_original.txt'>Click to open string_interactions_original.txt in new tab</a>")
download_link_string_filtered <- paste0("<a href='string_interactions_filtered.txt'>Click to open string_interactions_filtered.txt in new tab</a>")
download_link_string_properties <- paste0("<a href='string_network_properties.txt'>Click to open string_network_properties.txt in new tab</a>")
download_link_pathway_comparison <- paste0("<a href='pathway_comparison.txt'>Click to open pathway_comparison.txt in new tab</a>")
download_link_integrated_network <- paste0("<a href='integrated_network.txt'>Click to open integrated_network.txt in new tab</a>")
download_link_deg <- paste0("<a href='integrated_network.txt'>Click to open integrated_network.txt in new tab</a>")

cat(download_link_model, "<br>")
cat(download_link_final, "<br>")
cat(download_link_agents, "<br>")
cat(download_link_kegg_original, "<br>")
cat(download_link_kegg_filtered, "<br>")
cat(download_link_wp_original, "<br>")
cat(download_link_wp_filtered, "<br>")
cat(download_link_reactome_original, "<br>")
cat(download_link_reactome_filtered, "<br>")
cat(download_link_chea_original, "<br>")
cat(download_link_chea_filtered, "<br>")
cat(download_link_string_original, "<br>")
cat(download_link_string_filtered, "<br>")
cat(download_link_string_properties, "<br>")
cat(download_link_pathway_comparison, "<br>")
cat(download_link_integrated_network, "<br>")

```

## 11. Analysis Parameters
The following parameters were used for this analysis:

```{r load_params}, message=FALSE, warning=FALSE}

print("Experimental Design:")
cat(experimental_design)

# Load parameters from the saved file
params_file <- "analysis_parameters.txt"
if (file.exists(params_file)) {
  param_lines <- readLines(params_file)
  params <- list()
  for (line in param_lines) {
    parts <- strsplit(line, "=")[[1]]
    if (length(parts) == 2) {
      key <- trimws(parts[1])
      value <- trimws(parts[2])
      params[[key]] <- value
    }
  }
  
  # Display parameters in a table
  param_df <- data.frame(Parameter = names(params), Value = unlist(params))
  knitr::kable(param_df, caption = "Analysis Parameters", row.names = FALSE)
} else {
  cat("Parameters file not found. Please ensure 'analysis_parameters.txt' exists in the working directory.\n")
}
```


## 12. Session Info

```{r session_info, message=FALSE, warning=FALSE}
sessionInfo()
```